---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RPackage2

<!-- badges: start -->
<!-- badges: end -->

The goal of `RPackage2` is to provide examples of how to create an R package. `RPackage2` currently version `r packageVersion("RPackage2")` last built on `r packageDescription("RPackage2")$Built |> strsplit(";") |> magrittr::extract2(1) |> magrittr::extract2(3) |> as.Date() |> format("%d-%B-%Y")`. 

It includes functions for addition, multiplication, rolling dice, flipping coins, as well as some functions we utilized in the class such as counting missing columns. 

It also includes both an  [R6](https://adv-r.hadley.nz/r6.html#r6)`::`[R6Class](https://r6.r-lib.org/articles/Introduction.html) and [S4](https://adv-r.hadley.nz/s4.html) version of a deck of cards where we create a deck of cards, shuffling a deck, and drawing cards from the deck.

## Installation

You can install the development version of RPackage2 from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jkylearmstrong/RPackage2")
```

## Example

Here are some basic examples:

```{r example}
library(RPackage2)
```


### Arithmetic

```{r addition}
addition(1,2)
```

```{r multiplication}
multiplication(5,-4)
```

```{r composition}
multiplication(pi, complex(1,0,1)) |>
  exp() |>
  addition(1) # essentially 0, error due to floating point arithmetic
```

### Data Analysis

```{r}
mtcars |>
  missing_at_random() |>
  features_percent_miss()
```

```{r}
mtcars |>
  missing_at_random() |>
  features_percent_miss() |>
  plot()
```

```{r}
mtcars |>
  missing_at_random() |>
  missmap()
```

### Coin and Dice

```{r}
# Flip a coin 10 times
coin_flip(10)
```

```{r}
# Roll a 3-sided die 10 times
roll_dice(sides = 3, rolls = 10)
```

### Deck of Cards (R6)

```{r}
# Create a new deck
my_deck <- DeckOfCards$new()

# Shuffle the deck
my_deck$reshuffle()

# Draw cards
drawn_cards1 <- my_deck$draw(5)

# Print drawn cards
print(my_deck$drawn)

# should be the same
drawn_cards1 == my_deck$drawn

# Draw more cards
drawn_cards2 <- my_deck$draw(3)

# should be the same
rbind(drawn_cards1, drawn_cards2) == my_deck$drawn

# Print drawn cards
print(my_deck$drawn)
```

### Deck of Cards (S4)

```{r}
# Create a new deck
deck <- new("DeckOfCards4", setofcards = createDeck())

# Shuffle the deck
shuffled_deck <- shuffle(deck)

head(shuffled_deck@setofcards)

# Draw cards

result <- draw(deck, deck, 5)

# Print drawn cards
result
```
